---
title: "Comcast Complaints Support Analysis"
author: "Varun Chaturvedi"
date: "4/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Task Need to be performed:
- Importing  data into R environment.
- Provide the trend chart for the number of complaints at monthly and daily granularity levels.
- Provide a table with the frequency of complaint types.
-Which complaint types are maximum i.e., around internet, network issues, or across any other domains.
- Create a new categorical variable with value as Open and Closed. Open & Pending is to be categorized as Open and Closed & Solved is to be categorized as Closed.
- Provide state wise status of complaints in a stacked bar chart. Use the categorized variable from Q3. Provide insights on:
-Which state has the maximum complaints
-Which state has the highest percentage of unresolved complaints
- Provide the percentage of complaints resolved till date, which were received through theInternet and customer care calls.

```{r,message=FALSE}
# Including required Packages
library(stringi)
library(lubridate)
library(dplyr)
library(ggplot2)
```
- Loading Dataset:
```{r}
comcast_data<- read.csv("Comcast Telecom Complaints data.csv",header = TRUE)
#Manupulating column names
names(comcast_data)<- stri_replace_all(regex =  "\\.",replacement = "",str =names(comcast_data))
head(comcast_data)
```
Now data is loaded into R, now its available to process further.

- Finding NA`s in dataset:
```{r}
na_vector <- is.na(comcast_data)
length(na_vector[na_vector==T])
```
This shows There is  no missing values in dataset,so now data is tidy and available to process or do EDA based on requriment.

- Processing date.
```{r}
comcast_data$Date<- dmy(comcast_data$Date)
```
- Extracting monthly and daily 
```{r}
monthly_count<- summarise(group_by(comcast_data,Month =as.integer(month(Date))),Count = n())
daily_count<- summarise(group_by(comcast_data,Date),Count =n())
monthly_count<-arrange(monthly_count,Month)
#making count of monthly and daily compaints 
```
- Comparing Monthly and daily Complaints 
```{r,fig.height=4,fig.width=10}
ggplot(data = monthly_count,aes(Month,Count,label = Count))+
        geom_line()+
        geom_point(size = 0.8)+
        geom_text()+
        scale_x_continuous(breaks = monthly_count$Month)+
        labs(title = "Monthly Ticket Count",x= "Months",y ="No. of Tickets")
```
As we can see there is a incress in tickets in the month of **April,May** and this also increased in the month of **June**, so there might be some reseon due to that that they recived high amount of tickets.
```{r, fig.height=4,fig.width=10}
ggplot(data = daily_count,aes(as.POSIXct(Date),Count))+
        geom_line()+
        geom_point(size = 1)+
        scale_x_datetime(breaks = "2 weeks",date_labels = "%d/%m")+
        labs(title = "Daily Ticket Count",x= "Days",y ="No. of Tickets")
```
And if we see daily chart of tickets we find that in second half of **June** Month we recived more tickets with respect to normal days.